% resume.tex - My Resume using LaTex.

% Look and feel like Times New Roman
\documentclass[letterpaper,10pt]{article}
\usepackage[pass,letterpaper]{geometry}

\usepackage{mathptmx}
\usepackage{enumitem}

% Adjust margins
\addtolength{\oddsidemargin}{-.9in}
\addtolength{\evensidemargin}{-.9in}
\addtolength{\textwidth}{1.75in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.75in}

\begin{document}

% No extra spacing with lists
\setlist[itemize]{itemsep=0.0pt, topsep=0pt}

% No page number
\thispagestyle{empty}

% Title section
{\centering
  \textbf{{\fontsize{13}{15.6} \selectfont Andrew W. Boutin}}\\
  www.andrewboutin.com\par
}
\noindent
6 Meadow Lane
\hfill
(603) 558-3730\\
Amherst, NH 03031
\hfill
Andrew.w.boutin@gmail.com% This comment "protects" the end of line
\vspace{3pt}
\hrule
\vspace{\baselineskip}

% Employment section
\noindent
\textbf{EMPLOYMENT}
\vspace{5pt}
\hrule
\vspace{3pt}
\noindent\textbf{Software Engineer \& Certified ScrumMaster} - TimeTrade - Tewksbury, MA
\hfill
\textit{Dec 2016 –- Present}
\begin{itemize}
\setlength
  \item Focus on Micro-service REST API development with Spring, Spring Boot, \& Java for SaaS applications. Utilize technologies such as SQL, Docker, Gradle, SQL Server, PostgreSQL, JUnit, Mockito, Hamcrest, \& Postman.
  \item Own the Scrum process on a development team \& work closely with product owner.
  \item Architected \& implemented a solution for roles \& privileges into an auth-server.
  \item Initiated the integration of SAML functionality into an auth-server.
  \item Led effort to identify \& fix all continuous integration issues across all projects encompassing multiple version control, build, \& artifact tools such as GitHub, Jenkins Pipeline, \& Artifactory.
  \item Built an Amazon Alexa skill prototype integrated with AWS Lambda \& submitted a patent for review.
  \item Received the “Kicking Ass at TimeTrade” award for 2017 work performance.
\end{itemize}
\vspace{\baselineskip}

\noindent
\textbf{Software Development Engineer} - Dell Storage - Nashua, NH
\hfill
\textit{Feb 2015 –- Dec 2016}
\begin{itemize}
\setlength
  \item Created an internally hosted, Django powered, web application to house tools for developer use. Constructed several custom Python tools \& integrated them into the site.
  \item Drove the completion of a large infrastructure tool-set transition that impacted all of Dell Storage. Gathered requirements from managers, researched, designed solutions, wrote documentation, \& trained development teams.
  \item Developed a custom Java add-on, several Groovy scripts, \& JavaScript snippets to customize JIRA.
  \item Completed a data migration tool utilizing Java to ETL data from a SQL DB system to JIRA using its REST API.
  \item Mentored \& managed an intern through two summer internships.
  \item Administered JIRA, Stash, Confluence, \& Crowd instances.
  \item Received the Dell Champion, Dell Gold, \& Dell Bronze awards for various projects.
\end{itemize}
\vspace{\baselineskip}
\textbf{Intern Undergrad Sr. Analyst} - Dell Storage - Nashua, NH
\hfill
\textit{June 2014 –- Aug 2014}
\begin{itemize}
\setlength
  \item Implemented a new feature on an ASP.NET web application designed to ETL data from a DB by modifying each level of the MVC setup. Reported \& fixed other bugs during execution.
  \item Developed a Python system to calculate defect density by mining data from SQL DB \& Version Control systems \& storing data in a SQLite DB. Added a data view page to the existing ASP.NET system using C\#.
\end{itemize}
\vspace{\baselineskip}

\noindent
\textbf{Programming Intern/Technician} - iWorx Systems, Inc. - Dover, NH
\hfill
\textit{Jan 2013 –- Aug 2013}
\vspace{\baselineskip}

\noindent
\textbf{Corporal} - United States Marine Corps - Global
\hfill
\textit{Aug 2007 -– June 2011}
\vspace{\baselineskip}

% Education section
\noindent
\textbf{EDUCATION}
\vspace{5pt}
\hrule
\vspace{3pt}
\noindent\textbf{B.S. Computer Science, \textit{summa cum laude}} - University of New Hampshire
\hfill
\textit{2014}\\
\noindent\begin{tabular}{@{}l l}
  Awards: & Presidential Scholar, Dean’s List (all semesters).\\
  Scholarships: & Fred G. and Gertrude A. Howell Scholarship, Maurice Page Scholarship, Tony Grieco Scholarship.\\
\end{tabular}

\vspace{\baselineskip}
% Additional info section
\noindent
\textbf{ADDITIONAL INFO}
\vspace{5pt}
\hrule
\vspace{3pt}
\noindent\begin{tabular}{@{}l l}
  Website: & Launched a personal website using Django, Python, HTML, JavaScript, \& CSS.\\
  Video Games: & Worked on multiple games utilizing C\# \& the Unity engine.\\
  Mobile Apps: & Two Android apps using Java \& SQLite - 1 personal, 1 collaborative project.\\
  Experience with: & Git, version control systems, build tools, code reviews, testing, various IDEs.\\
  Operating Systems: & Windows, Linux, \& Mac.
\end{tabular}

\end{document}
